Machine Learning Working Notes

### 2016-11-03 ml_notes/draft.tex
- change to new MBP

\subsection{Classification}
Now let us consider classification problem, where we expect a functional $ \pi(\vct x) $ to map input to class labels, in binary case $ \vct y=\left\{ +1, -1 \right\} $.

>>>>

\subsection{Classification}
Now let us consider classification problem, where we expect a functional $ \pi(\vct x) $ to map input $ \vct x $ to class labels, in binary case $ \vct y=\left( +1, -1 \right) $. More commonly, we can define a Bernoulli distribution $ p(y=+1 \mid x) $ for one class and $ 1-p\left( y=+1 \mid x \right) $ for another. Typically, we would choose a sigmoid function, \eg logistic function or \textit{tanh} to warp a possibly infinite value into a bounding box, \eg, $ \left\lbrack 0, 1 \right\rbrack $ for logistic function. This is a desired behavior, since any function value will be transformed to a probability. A logistic function is defined,
\[ \sigma(a) = \frac{1}{1+\exp(-a)} \]
Obviously, we also have, 
\begin{align*}
\sigma(-a) = 1-\sigma(a) \\
\tanh(a) = 2\sigma(2a) -1 \\
\diff{\sigma(a)}{a} = \left( 1-\sigma(a) \right)\sigma(a)
\end{align*}
Thus, the conditional class distribution given input dataset can be defined as a sigmoid function on the linear model $ p\left( y \mid \vct x \right) = \sigma(yf(\vct x))$, again we fold the bias term $ b $ in the parameters $ \vct w $.
